Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-08-14 Manuscript/manuscriptPSsuppl.tex
Update SI

\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/PS_labels.png}
  \includegraphics[width=16.0cm]{../Figs/figS7.png}
  \caption{\label{dihedralsHG}
    Dihedral angle distributions of headgroup region of PS lipids from different simulation models.
  }
\end{figure*}

@@

\section{Calcium bindinf to POPC in CHARMM36 simulation with NBfix}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/OP_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{OP_CHARMM_CaCl_POPC_NBFix}
  The response of headgroup order parameters to the fixed amount of cationic surfactants in
  POPC bilayer is compared between simulations and experiments \cite{scherer89}.}
\end{figure}

>>>>

\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/PS_Labels.png}
  \includegraphics[width=16.0cm]{../Figs/figS7.png}
  \caption{\label{dihedralsHG}
    Dihedral angle distributions of headgroup region of PS lipids from different simulation models.
  }
\end{figure*}

@@

\section{Calcium binding to POPC in CHARMM36 simulation with NBfix}

The response of headgroup order parameters to the CaCl$_2$ concentration
are underestimated in simulations with CHARMM36 with the NBfix term emloyed
to the interactions between calicum and lipid oxygens \cite{kim16}
(Fig. \ref{changesWITHCaClPS} in the main text),
indicating that the calcium binding to the bilayer is too weak with these
parameters. Without the NBfix term, the calcium binding affinity to PC
lipid bilayers was overestimated in the CHARMM36 model \cite{catte16}.
However, after employing the NBfix term, the response of headgroup order
parameters (Fig. \ref{OP_CHARMM_CaCl_POPC_NBFix}) and the binding affinity
(Fig. \ref{density_profile_CHARMM_CaCl_POPC_NBFix}) of calcium also to
POPC bilayer are underestimated. Notably, the CHARMM36 simulations with NBfix
terms predict similar binding affinity to sodium and calcium.
In conclusion, the special NBfix~\cite{kim16} for calcium, 
incorporated in the parameters give by the CHARMM-GUI at the time
of running the simulations (January 2018), leads to the underestimation
calcium binding affinity to PC and PS lipid bilayers.

\begin{figure}[]
  \centering
  \includegraphics[width=17.0cm]{../Figs/OP_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{OP_CHARMM_CaCl_POPC_NBFix}
    Simulation files for CHARMM36 with the NBfix term in calcium are available from Ref. \citenum{CHARMM36withCaClNBfix}.
  }
\end{figure}
